moduleoneanalysis

### 2023-09-20 module1/moduleoneanalysis.Rmd
governance preference graphs
updating rmd file with clean data
lot of changes because I wasn't opening the project file.

---
title: "moduleoneanalysis"
output:
  html_document:
    fig_width: 7
    fig_height: 6
    fig_caption: true
    keep_md: true
    theme: paper
    df_print: paged
---

```{r load packages, warning = FALSE, message = FALSE}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(dplyr))

@@

```{r, eval=TRUE}

moduleone <- read_excel(here::here("thesis_surveydata/livelihood_insecurity_complete.xlsx"))
save(moduleone, file = "moduleone.rda")
module1 <- data.frame(moduleone)
module1 %>%
  filter(!row_number() %in% c(1,2))

@@

```{r, eval =TRUE}
#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
codedmodule1 <- module1 %>%

#remove row 1
  filter(!row_number() %in% c(1,2)) %>%

# replace risky likert scale with numbers
  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
                                                       . =="Slightly risky" ~ 2, 
                                                       . =="Moderately risky" ~ 3, 
                                                       . =="Very risky" ~ 4, 
                                                       . =="Extremely risky" ~ 5))) %>%

# replace beneficial likert scale with numbers  
  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
                                                     . =="Slightly beneficial" ~ 2,
                                                     . =="Moderately beneficial" ~ 3,
                                                     . =="Very beneficial" ~ 4,
                                                     . =="Extremely beneficial" ~ 5 ))) %>%

# replace nuclear acceptance likert scale with numbers
  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                        . == "Somewhat disagree" ~ 2,
                                                                        . == "Neither agree nor disagree" ~3,
                                                                        . == "Somewhat agree" ~ 4,
                                                                        . == "Strongly agree" ~ 5))) %>%

  mutate_at(vars(Livelihood_Income), funs(case_when(. == "(a) own farming/fishing/animal rearing/business" ~ "LSI", 
                                                    . == "(b) employed for wages/salary" ~ "ISI",
                                                    . == "(c) student" ~"student",
                                                    . == "(d) currently unemployed" ~ "unemployed",
                                                    . == "(e) homemaker" ~ "homemaker",
                                                    . == "(f) retired" ~ "retired",
                                                    . == "(g) unable to work" ~ "unable to work" ))) %>%

# coding education
   mutate_at(vars(education), funs(case_when(. == "No schooling completed" ~ 0, 
                                                                        . == "Primary school" ~ 1,
                                                                        . == "Grade 10th" ~ 2,
                                                                        . == "Grade 12th" ~ 3,
                                                                        . == "Some college, no degree" ~ 4,
                                                                        . == "Trade/technical/vocational training" ~ 5,
                                                                        . == "Bachelor's degree" ~ 6,
                                                                        . == "Master's degree" ~ 7,
                                                                        . == "Professional degree" ~ 8,
                                                                        . == "Doctorate degree" ~ 9 ))) %>%
# coding yes and no questions
  mutate_at(vars(Iassociation, govtscheme, wateravail, polposition, polparty), funs(case_when(.== "Yes" ~ 1,
                                            .== "No" ~ 0))) %>%
# reverse coding yes and no questions
  mutate_at(vars(illness,severeillness), funs(case_when(.== "Yes" ~ 0,
                                            .== "No" ~ 1))) %>%

# coding How confident are you that you can continue your current livelihood if you want to? 
 mutate_at(vars(Lconfidence), funs(case_when(. == "Not at all confident" ~ 1, 
                                                                        . == "Not much confident" ~ 2,
                                                                        . == "Neutral" ~3,
                                                                        . == "Somewhat confident" ~ 4,
                                                                        . == "Very confident" ~ 5))) %>%

 mutate_at(vars(Lboat, houseown), funs(case_when(.== "Own it" ~ 1,
                                                 .== "Rent it" ~ 0)))%>%

# J security index coding

 mutate_at(vars(JISRkeep), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                        . == "Somewhat disagree" ~ 2,
                                                                        . == "Neither agree nor disagree" ~3,
                                                                        . == "Somewhat agree" ~ 4,
                                                                        . == "Strongly agree" ~ 5))) %>%

# reverse code JIS 
  mutate_at(vars(JISlosefuture, JISlose, JISfuture), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                                        . == "Somewhat disagree" ~ 4,
                                                                        . == "Neither agree nor disagree" ~3,
                                                                        . == "Somewhat agree" ~ 2,
                                                                        . == "Strongly agree" ~ 1))) %>%

  mutate_at(vars(totalincome, otherincome), funs(case_when(. == "Less than Rs 1,00,000" ~ 1,
                                                                        . == "Rs 1,00,000 to Rs 2,50,000"  ~ 2,
                                                                        . == "Rs 2,50,001 to Rs 5,00,000" ~ 3,
                                                                        . == "Rs 5,00,001 to Rs 10,00,000" ~ 4,
                                                                        . == "Rs 10,00,001 and above"  ~ 5))) %>%

  mutate_at(vars(workknowledge, subsidyknow), funs(case_when(. == "Very poor" ~ 1, 
                                                                        . == "Poor" ~ 2,
                                                                        . == "Fair" ~3,
                                                                        . == "Good" ~ 4,
                                                                        . == "Very good" ~ 5))) %>%

mutate_at(vars(drinkingwater, cookingwater), funs(case_when(. == "Bottled water/ Filtered Water" ~ 1,                                       
                                                          .  == "Piped into dwelling" ~ 2,                                                  
                                                          .  == "Piped to neighbour" ~ 3,                                                   
                                                          .  == "Piped to yard/plot" ~ 4, 
                                                          .  == "Protected well" ~ 5, 
                                                          .  == "Public tap/standpipe" ~6,
                                                          .  == "Surface Water  (River/Dam/Lake/Pond/Stream/Canal/Irrigation Channel)" ~7, 
                                                          .  == "Tanker Truck" ~ 8,
                                                          .  == "Tubewell/borehole" ~ 9,
                                                          .  == "Unprotected Spring" ~ 10))) %>%

  mutate_at(vars(toilet), funs(case_when(. == "No facility/bush/field" ~ 1,                                       
                                                          .  == "Hanging toilet/hanging latrine" ~ 2,                                             
                                                          .  == "Bucket toilet"  ~ 3,                                                   
                                                          .  == "Composting toilet"  ~ 4, 
                                                          .  == "Pit latrine without slab/open pit" ~ 5, 
                                                          .  == "Pit latrine with slab" ~6,
                                                          .  == "Ventilated improved pit laterine"  ~7, 
                                                          .  == "Flush to somewhere else"  ~ 8,
                                                          .  == "Flush to pit latrine"  ~ 9,
                                                          .  == "Flush to septic tank" ~ 10,
                                                          .  == "Flush to piped sewer system" ~ 11))) %>%

  mutate_at(vars(house), funs(case_when(. == "Hut made of mud, bamboo, straw etc. (kutcha house)" ~ 1, 
                                        . == "Permanent single story house (pukka house)" ~ 2,
                                        . == "Apartment/Flat in a multi-story building"  ~3,
                                        . == "Multi-story house" ~ 4))) %>%

  mutate_at(vars(foodtrouble), funs(case_when(. == "8 or more months" ~ 1,                                       
                                                          .  == "6-8 months"  ~ 2,                                                  
                                                          .  == "4-6 months"  ~ 3,                                                   
                                                          .  == "2-4 months"  ~ 4, 
                                                          .  == "1-2 months" ~ 5, 
                                                          .  == "0 months"  ~6))) %>%

   mutate_at(vars(foodadequacy), funs(case_when(. == "Extremely inadequate" ~ 1, 
                                                                        . == "Moderately inadequate" ~ 2,
                                                                        . == "Slightly inadequate" ~3,
                                                                        . == "Neither adequate nor inadequate" ~ 4,
                                                                        . == "Slightly adequate" ~ 5,
                                                                        . == "Moderately adequate" ~ 6,
                                                                        . == "Extremely adequate" ~ 7)))%>%

separate( col = cookstove, into = c("cook1", "cook2", "cook3", "cook4"), sep = ",") %>%
separate( col = vehicle, into = c("vehicle1", "vehicle2", "vehicle3", "vehicle4"), sep = ",")%>%
separate( col = foodsource, into = c("food1", "food2", "food3", "food4"), sep = ",")

#coded dependent variables for module 1 livelihood and income security survey

codedmodule1
```

```{r}
# solving the problem of multiple answers  to a questions 
codedmodule1

@@

```{r}

x <- as.factor(codedmodule1$vehicle)

levels(x)

@@

```{r}

@@

```{r}

@@

>>>>

---
title: "moduleoneanalysis"
output:
  pdf_document: default
  html_document:
    fig_width: 7
    fig_height: 6
    fig_caption: yes
    keep_md: yes
    theme: paper
    df_print: paged
---

```{r load packages, warning = FALSE, message = FALSE}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(psych))

@@

```{r, eval=TRUE, echo = FALSE}

moduleone <- read_excel(here::here("thesis_surveydata/livelihood_insecurity_complete.xlsx"))
save(moduleone, file = "moduleone.rda")
module1 <- data.frame(moduleone)

@@

```{r, warning = FALSE, echo = FALSE}
#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
codedmodule1 <- module1 %>%
  #remove row 1
  filter(!row_number() %in% c(1,2)) %>%

  # replace risky likert scale with numbers
  mutate(across(starts_with("Risky"), ~case_when(. =="Not at all risky" ~ 1, 
                                                 . =="Slightly risky" ~ 2, 
                                                 . =="Moderately risky" ~ 3, 
                                                 . =="Very risky" ~ 4, 
                                                 . =="Extremely risky" ~ 5))) %>%

  # replace beneficial likert scale with numbers  
  mutate(across(starts_with("Ben"), ~case_when(. =="Not at all beneficial" ~ 1,
                                               . =="Slightly beneficial" ~ 2,
                                               . =="Moderately beneficial" ~ 3,
                                               . =="Very beneficial" ~ 4,
                                               . =="Extremely beneficial" ~ 5 ))) %>%

  # replace nuclear acceptance likert scale with numbers
  mutate(across(c(N_accept,N_reluctantlyaccept,N_reject), ~case_when(. == "Strongly disagree" ~ 1, 
                                                                     . == "Somewhat disagree" ~ 2,
                                                                     . == "Neither agree nor disagree" ~3,
                                                                     . == "Somewhat agree" ~ 4,
                                                                     . == "Strongly agree" ~ 5))) %>%

  mutate(across(Livelihood_Income, ~case_when(. == "(a) own farming/fishing/animal rearing/business" ~ "LSI", 
                                              . == "(b) employed for wages/salary" ~ "ISI",
                                              . == "(c) student" ~"other",
                                              . == "(d) currently unemployed" ~ "other",
                                              . == "(e) homemaker" ~ "homemaker",
                                              . == "(f) retired" ~ "other",
                                              . == "(g) unable to work" ~ "other" ))) %>%

  # coding education
  mutate(across(education, ~case_when(. == "No schooling completed" ~ 0, 
                                      . == "Primary school" ~ 1,
                                      . == "Grade 10th" ~ 2,
                                      . == "Grade 12th" ~ 3,
                                      . == "Some college, no degree" ~ 4,
                                      . == "Trade/technical/vocational training" ~ 5,
                                      . == "Bachelor's degree" ~ 6,
                                      . == "Master's degree" ~ 7,
                                      . == "Professional degree" ~ 8,
                                      . == "Doctorate degree" ~ 9 ))) %>%

  # coding yes and no questions
  mutate(across(c(Lassociation,Iassociation, govtscheme, wateravail, polposition, polparty), ~case_when(.== "Yes" ~ 1,
                                                                                                        .== "No" ~ 0))) %>%
  # reverse coding yes and no questions
  mutate(across(c(illness,severeillness), ~case_when(.== "Yes" ~ 0,
                                                     .== "No" ~ 1))) %>%

  # coding How confident are you that you can continue your current livelihood if you want to? 
  mutate(across(Lconfidence, ~case_when(. == "Not at all confident" ~ 1, 
                                        . == "Not much confident" ~ 2,
                                        . == "Neutral" ~3,
                                        . == "Somewhat confident" ~ 4,
                                        . == "Very confident" ~ 5))) %>%

  mutate(across(c(Lboat, houseown), ~case_when(.== "Own it" ~ 1,
                                               .== "Rent it" ~ 0))) %>%

  # J security index coding
  mutate(across(JISRkeep, ~case_when(. == "Strongly disagree" ~ 1, 
                                     . == "Somewhat disagree" ~ 2,
                                     . == "Neither agree nor disagree" ~3,
                                     . == "Somewhat agree" ~ 4,
                                     . == "Strongly agree" ~ 5))) %>%

  # reverse code JIS 
  mutate(across(c(JISlosefuture, JISlose, JISfuture), ~case_when(. == "Strongly disagree" ~ 5, 
                                                                 . == "Somewhat disagree" ~ 4,
                                                                 . == "Neither agree nor disagree" ~3,
                                                                 . == "Somewhat agree" ~ 2,
                                                                 . == "Strongly agree" ~ 1))) %>%

  mutate(across(c(totalincome, otherincome), ~case_when(. == "Less than Rs 1,00,000" ~ 1,
                                                        . == "Rs 1,00,000 to Rs 2,50,000"  ~ 2,
                                                        . == "Rs 2,50,001 to Rs 5,00,000" ~ 3,
                                                        . == "Rs 5,00,001 to Rs 10,00,000" ~ 4,
                                                        . == "Rs 10,00,001 and above"  ~ 5,
                                                        . == "Doesn't apply" ~ 0))) %>%

  mutate(across(c(workknowledge, subsidyknow), ~case_when(. == "Very poor" ~ 1, 
                                                          . == "Poor" ~ 2,
                                                          . == "Fair" ~3,
                                                          . == "Good" ~ 4,
                                                          . == "Very good" ~ 5))) %>%

  mutate(across(c(drinkingwater, cookingwater), ~case_when(. == "Bottled water/ Filtered Water" ~ 1,                                       
                                                           .  == "Piped into dwelling" ~ 2,                                                  
                                                           .  == "Piped to neighbour" ~ 3,                                                   
                                                           .  == "Piped to yard/plot" ~ 4, 
                                                           .  == "Protected well" ~ 5, 
                                                           .  == "Public tap/standpipe" ~6,
                                                           .  == "Surface Water  (River/Dam/Lake/Pond/Stream/Canal/Irrigation Channel)" ~7, 
                                                           .  == "Tanker Truck" ~ 8,
                                                           .  == "Tubewell/borehole" ~ 9,
                                                           .  == "Unprotected Spring" ~ 10))) %>%

  mutate(across(toilet, ~case_when(. == "No facility/bush/field" ~ 1,                                       
                                   .  == "Hanging toilet/hanging latrine" ~ 2,                                             
                                   .  == "Bucket toilet"  ~ 3,                                                   
                                   .  == "Composting toilet"  ~ 4, 
                                   .  == "Pit latrine without slab/open pit" ~ 5, 
                                   .  == "Pit latrine with slab" ~6,
                                   .  == "Ventilated improved pit laterine"  ~7, 
                                   .  == "Flush to somewhere else"  ~ 8,
                                   .  == "Flush to pit latrine"  ~ 9,
                                   .  == "Flush to septic tank" ~ 10,
                                   .  == "Flush to piped sewer system" ~ 11))) %>%

  mutate(across(house, ~case_when(. == "Hut made of mud, bamboo, straw etc. (kutcha house)" ~ 1, 
                                  . == "Permanent single story house (pukka house)" ~ 2,
                                  . == "Apartment/Flat in a multi-story building"  ~3,
                                  . == "Multi-story house" ~ 4))) %>%

  mutate(across(foodtrouble, ~case_when(. == "8 or more months" ~ 1,                                       
                                        .  == "6-8 months"  ~ 2,                                                  
                                        .  == "4-6 months"  ~ 3,                                                   
                                        .  == "2-4 months"  ~ 4, 
                                        .  == "1-2 months" ~ 5, 
                                        .  == "0 months"  ~6))) %>%

  mutate(across(foodadequacy, ~case_when(. == "Extremely inadequate" ~ 1, 
                                         . == "Moderately inadequate" ~ 2,
                                         . == "Slightly inadequate" ~3,
                                         . == "Neither adequate nor inadequate" ~ 4,
                                         . == "Slightly adequate" ~ 5,
                                         . == "Moderately adequate" ~ 6,
                                         . == "Extremely adequate" ~ 7))) %>%

  # separating cooking, vehicle and food cols into separate entries
  separate(col = cookstove, into = c("cook1", "cook2", "cook3", "cook4"), sep = ",") %>%
  separate(col = vehicle, into = c("vehicle1", "vehicle2", "vehicle3", "vehicle4"), sep = ",") %>%
  separate(col = foodsource, into = c("food1", "food2", "food3", "food4"), sep = ",") %>%

  mutate(across(c(cook1, cook2, cook3, cook4), ~case_when(. == "Three Stone Stove/Open Fire" ~ 1, 
                                  . == "Traditional Solid Fuel Stove" ~ 2,
                                  . == "Liquid Fuel Stove" ~3,
                                  . == "Biogas Stove" ~ 4,
                                  . == "Piped Natural Gas Stove" ~ 5,
                                  . == "Liquefied Petroleum Gas (LPG)/Cooking gas stove" ~ 6,
                                  . == "Solar Cooker" ~ 7,
                                  . == "Electric Stove" ~ 7,
                                  is.na(.) ~ 0))) %>%

  mutate(across(c(vehicle1, vehicle2, vehicle3, vehicle4, vehicletext), ~case_when(. == "Bicycle" ~ 1, 
                                    . == "Animal Drawn Cart" ~ 2,
                                    . == "Motorcycle/Scooter" ~3,
                                    . == "Car" ~ 4,
                                    . == "Truck" ~ 4,
                                    . == "Boat with Motor" ~ 4,
                                    . == "Tractor" ~ 4,
                                    . == "E-rickshaw" ~ 1,
                                    . == "Tempo" ~ 3,
                                    . == "Nothing" ~ 0,
                                    . == "Other (Please Specify)" ~ 0,
                                    is.na(.) ~ 0))) %>%

  mutate(across(c(food1, food2, food3,food4), ~case_when(. == "Forest" ~ 1, 
                                  . == "Own Farm" ~ 2,
                                  . == "Market" ~4,
                                  . == "Own livestock" ~ 2,
                                  . == "Subsidised ration shops" ~ 3,
                                  is.na(.) ~ 0)))

codedmodule1$gender <- factor(codedmodule1$gender, levels = c("Male","Female"))

#converting relevant variables to factors 
#codedmodule1 <- codedmodule1 %>%
  #mutate_at(vars(Lassociation, Lboat, Iassociation, totalincome, otherincome, govtscheme, education, subsidyknow, drinkingwater, cookingwater, wateravail, toilet,
                # house, houseown, cook1, cook2, cook3, cook4, vehicle1, vehicle2, vehicle3, vehicle4, vehicletext, polposition, polparty,  food1, food2, food3, food4, foodadequacy, foodtrouble, #illness, severeillness, age, urban_rural, gender, caste, religion), 
                 #~factor(.))
#converting relevant variables to Numeric

@@

```{r, echo=FALSE}

colnames(codedmodule1)
addedcols <- codedmodule1 %>%
  mutate_at(vars(Lassociation, Lboat, Iassociation, totalincome, otherincome, govtscheme, education, subsidyknow, drinkingwater, cookingwater, wateravail, toilet, house, houseown, cook1, cook2, cook3, cook4, vehicle1, vehicle2, vehicle3, vehicle4, vehicletext, polposition, polparty, food1, food2, food3, food4, foodadequacy, foodtrouble, illness, severeillness, Llenght, Lfarmbigha, Lanimalcowbull, Lanimalcattle, Lanimalhorses, Lanimalgoats, Lanimalsheep, Lanimalpoultry, Ilenght, Ipropvalue, farwatermins, healthdist), as.numeric) %>%
  mutate(stove = cook1 + cook2 + cook3 + cook4, 
        vehicle = vehicle1 + vehicle2 + vehicle3 + vehicle4 + vehicletext,
        food = food1 + food2 + food3 + food4,
        #income = totalincome + otherincome,
        animals = Lanimalcowbull + Lanimalcattle + Lanimalhorses + Lanimalgoats + Lanimalsheep + Lanimalpoultry) %>%
  dplyr::select(-cook1, -cook2, -cook3, -cook4, -vehicle1, -vehicle2, -vehicle3, -vehicle4, -vehicletext, -food1, -food2, -food3, -food4, -Lanimalcowbull, -Lanimalcattle, -Lanimalhorses, -Lanimalgoats, -Lanimalsheep, -Lanimalpoultry) %>%
  unite("LIlenght", c(Llenght,Ilenght), na.rm = TRUE, remove = TRUE)%>%
  unite("LIassociation", c(Lassociation,Iassociation), na.rm = TRUE, remove = TRUE)

@@

\newpage

The total n for this survey is 1062. However, the sample is divided by the type of work people do as below:

```{r, echo=FALSE}

count <- module1 %>% count(Livelihood_Income)

count <- count[1:(nrow(count) - 2), ]

count

@@

# The Problem of large NAs

```{r, echo=FALSE}

# Count the number of NAs in each column
num_NAs <- colSums(is.na(addedcols))

# Print the result
print(num_NAs)

@@

```{r, echo = FALSE}

nuclear_LI <- addedcols %>% 
  dplyr::select(Risky_Nuclear,State, gender, caste, religion, urban_rural, age,  Livelihood_Income,education, workknowledge,LIlenght, subsidyknow, drinkingwater,cookingwater,farwatermins, wateravail,toilet, house,stove, vehicle, houseown, polposition, LIassociation,polparty, govtscheme, totalincome, Lfarmbigha,  Ipropvalue, Lboat, animals, foodadequacy, foodtrouble,food, healthdist, illness, severeillness)

# checking NAs in LSI part 
assetcheck <- addedcols %>% filter(Livelihood_Income == "LSI") %>%
            dplyr::select(Lfarmland,Lfarmbigha,animals)

num_NAs2 <- colSums(is.na(assetcheck))

#print(num_NAs2)

codedmodule1 %>% count(Livelihood_Income)
addedcols %>% count(Livelihood_Income)
codedmodule1 %>% count(Lfarmbigha)
codedmodule1 %>% filter(Livelihood_Income == "LSI") %>% count(Lfarmland)
addedcols %>% filter(Livelihood_Income == "LSI") %>% count(animals)
codedmodule1 %>% count(Lboat)

addedcols %>% filter(Livelihood_Income == "LSI") %>% filter(Lfarmland == "Doesn't apply") %>% count(Lboat)
addedcols %>% filter(Livelihood_Income == "LSI") %>% filter(Lfarmland == "Doesn't apply") %>% count(animals)

addedcols %>% filter(Livelihood_Income == "ISI") %>% count(Iproperty)

# checking NAs in ISI part

module1 %>% filter(!row_number() %in% c(1,2)) %>% filter(Livelihood_Income != "(a) own farming/fishing/animal rearing/business") %>% count(Iproperty)

# there are only 4 people who said they own a boat but not a farmland when looking at those people who answered LSI part of the survey. So we will just look at boat as  another livelihood asset and remove the 4 responses by removing Doesn't apply values in the Lfarmland part.

```{r, echo = FALSE}
# Nuclear dataframe for LSI/ISI with standardized values

# Convert columns to numeric starting from 'education'
cols_to_convert <- names(nuclear_LI)[which(names(nuclear_LI) == 'education'):length(names(nuclear_LI))]
nuclear_LI[cols_to_convert] <- lapply(nuclear_LI[cols_to_convert], as.numeric)

nuclear_LI$LIassociation <- as.numeric(nuclear_LI$LIassociation)
nuclear_LI$LIlenght <- as.numeric(nuclear_LI$LIlenght)
# Standardize the values
standardize <- function(x) {
  (x - min(x, na.rm = TRUE)) / (max(x, na.rm = TRUE) - min(x, na.rm = TRUE))
}

nuclear_LI[cols_to_convert] <- lapply(nuclear_LI[cols_to_convert], standardize)

# Displaying the first few rows of the dataframe
#head(nuclear_LI)

```{r, echo = FALSE}

# first make two different groups in the data by Livelihood_Income variable. - homemaker, ISI, LSI, other (retired, student, unable to work, unemployed)

str(nuclear_LI)

# For 'homemaker'
homemaker_df <- nuclear_LI %>% filter(Livelihood_Income == "homemaker") %>%
                dplyr::select (Risky_Nuclear, State,education, workknowledge, LIlenght, drinkingwater,cookingwater,farwatermins, wateravail,toilet, house,stove, vehicle, houseown, polposition, LIassociation, polparty, govtscheme, totalincome, foodadequacy, foodtrouble,food, healthdist, illness, severeillness) %>%
  na.omit()

num_NAs3 <- colSums(is.na(homemaker_df))

# For 'ISI'
ISI_df <- nuclear_LI %>% filter(Livelihood_Income == "ISI") %>%
  dplyr::select(Risky_Nuclear,State, education, workknowledge,LIlenght, drinkingwater,cookingwater,farwatermins, wateravail,toilet, house,stove, vehicle, houseown, polposition, LIassociation,polparty, govtscheme, totalincome, foodadequacy, foodtrouble,food, healthdist, illness, severeillness) %>%
   na.omit()

num_NAs4 <- colSums(is.na(ISI_df))

# For 'LSI'
LSI_df <- nuclear_LI %>% filter(Livelihood_Income == "LSI")  %>% 
  dplyr::select(Risky_Nuclear,State, education, workknowledge,LIlenght, drinkingwater,cookingwater,farwatermins, wateravail,toilet, house,stove, vehicle, houseown, polposition, LIassociation,polparty, govtscheme, totalincome, animals, foodadequacy, foodtrouble,food, healthdist, illness, severeillness) %>%
  na.omit()

num_NAs5 <- colSums(is.na(LSI_df))

# For 'other'
other_df <- nuclear_LI %>% filter(Livelihood_Income == "other")%>% 
  dplyr::select(Risky_Nuclear,State, education, workknowledge,LIlenght, drinkingwater,cookingwater,farwatermins, wateravail,toilet, house,stove, vehicle, houseown, polposition, LIassociation,polparty, govtscheme, totalincome, foodadequacy, foodtrouble,food, healthdist, illness, severeillness)%>%
  na.omit()

num_NAs6 <- colSums(is.na(other_df))

# problem of small sample size - how to deal with it ?

```{r, echo = FALSE}

library(dplyr)

# now aggregating LSI/ISI for different groups.

homemaker <- homemaker_df %>%
  mutate(
    human_asset = rowMeans(dplyr::select(., education, workknowledge, LIlenght), na.rm = TRUE),
    physical_asset = rowMeans(dplyr::select(., drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown), na.rm = TRUE),
    social_asset = rowMeans(dplyr::select(., polposition, LIassociation, polparty, govtscheme), na.rm = TRUE),
    financial_asset = totalincome,
    food_security = rowMeans(dplyr::select(., foodadequacy, foodtrouble, food), na.rm = TRUE),
    health_status = rowMeans(dplyr::select(., healthdist, illness, severeillness), na.rm = TRUE)
  )%>%
 dplyr::select(
    -c(education, workknowledge, LIlenght, 
      drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown, 
      polposition, LIassociation, polparty, govtscheme, 
      foodadequacy, foodtrouble, food,
      healthdist, illness, severeillness,
      totalincome)
  )%>%
  mutate(
    score = rowMeans(dplyr::select(., human_asset, physical_asset, social_asset, financial_asset, food_security, health_status), na.rm = TRUE)
  )

ISI <- ISI_df%>%
  mutate(
    human_asset = rowMeans(dplyr::select(., education, workknowledge, LIlenght), na.rm = TRUE),
    physical_asset = rowMeans(dplyr::select(., drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown), na.rm = TRUE),
    social_asset = rowMeans(dplyr::select(., polposition, LIassociation, polparty, govtscheme), na.rm = TRUE),
    financial_asset = totalincome,
    food_security = rowMeans(dplyr::select(., foodadequacy, foodtrouble, food), na.rm = TRUE),
    health_status = rowMeans(dplyr::select(., healthdist, illness, severeillness), na.rm = TRUE)
  )%>%
  dplyr::select(
    -c(education, workknowledge, LIlenght, 
      drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown, 
      polposition, LIassociation, polparty, govtscheme, 
      foodadequacy, foodtrouble, food,
      healthdist, illness, severeillness,
      totalincome)
  )%>%
  mutate(
    score = rowMeans(dplyr::select(., human_asset, physical_asset, social_asset, financial_asset, food_security, health_status), na.rm = TRUE)
  )

LSI <- LSI_df%>%
  mutate(
    human_asset = rowMeans(dplyr::select(., education, workknowledge, LIlenght), na.rm = TRUE),
    physical_asset = rowMeans(dplyr::select(., drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown), na.rm = TRUE),
    social_asset = rowMeans(dplyr::select(., polposition, LIassociation, polparty, govtscheme), na.rm = TRUE),
    financial_asset = totalincome,
    food_security = rowMeans(dplyr::select(., foodadequacy, foodtrouble, food), na.rm = TRUE),
    health_status = rowMeans(dplyr::select(., healthdist, illness, severeillness), na.rm = TRUE)
  )%>%
  dplyr::select(
    -c(education, workknowledge, LIlenght, 
      drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown, 
      polposition, LIassociation, polparty, govtscheme, 
      foodadequacy, foodtrouble, food,
      healthdist, illness, severeillness,
      totalincome)
  )%>%
  mutate(
    score = rowMeans(dplyr::select(., human_asset, physical_asset, social_asset, financial_asset, food_security, health_status), na.rm = TRUE)
  )

other <- other_df%>%
  mutate(
    human_asset = rowMeans(dplyr::select(., education, workknowledge, LIlenght), na.rm = TRUE),
    physical_asset = rowMeans(dplyr::select(., drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown), na.rm = TRUE),
    social_asset = rowMeans(dplyr::select(., polposition, LIassociation, polparty, govtscheme), na.rm = TRUE),
    financial_asset = totalincome,
    food_security = rowMeans(dplyr::select(., foodadequacy, foodtrouble, food), na.rm = TRUE),
    health_status = rowMeans(dplyr::select(., healthdist, illness, severeillness), na.rm = TRUE)
  )%>%
  dplyr::select(
    -c(education, workknowledge, LIlenght, 
      drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown, 
      polposition, LIassociation, polparty, govtscheme, 
      foodadequacy, foodtrouble, food,
      healthdist, illness, severeillness,
      totalincome)
  )%>%
  mutate(
    score = rowMeans(dplyr::select(., human_asset, physical_asset, social_asset, financial_asset, food_security, health_status), na.rm = TRUE)
  )

```{r, echo = FALSE}

# lms now for each category and then putting them into a single table using stargazer

nuclear_model <- nuclear_LI %>%  
  mutate(
    human_asset = rowMeans(dplyr::select(., education, workknowledge, LIlenght), na.rm = TRUE),
    physical_asset = rowMeans(dplyr::select(., drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown), na.rm = TRUE),
    social_asset = rowMeans(dplyr::select(., polposition, LIassociation, polparty, govtscheme), na.rm = TRUE),
    financial_asset = totalincome,
    food_security = rowMeans(dplyr::select(., foodadequacy, foodtrouble, food), na.rm = TRUE),
    health_status = rowMeans(dplyr::select(., healthdist, illness, severeillness), na.rm = TRUE)
  )%>%
  dplyr::select(
    -c(education, workknowledge, LIlenght, 
      drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown, 
      polposition, LIassociation, polparty, govtscheme, 
      foodadequacy, foodtrouble, food,
      healthdist, illness, severeillness,
      totalincome, Lfarmbigha, Ipropvalue, Lboat, animals)
  )%>%
  mutate(LIscore = rowMeans(dplyr::select(., human_asset, physical_asset, social_asset,financial_asset, food_security,health_status), na.rm = TRUE))

nuclearLI_lm <- lm(Risky_Nuclear ~ caste + gender + urban_rural + human_asset + physical_asset + social_asset + financial_asset + food_security + health_status , data = nuclear_model)

nuclearLI_lm2 <- lm(Risky_Nuclear ~ caste + gender + urban_rural + LIscore , data = nuclear_model)

summary(nuclearLI_lm)
summary(nuclearLI_lm2)
#plot(nuclearLI_lm)

```{r, echo=FALSE}
solar_LI <- addedcols %>% 
  dplyr::select(Risky_Solar,State, gender, caste, religion, urban_rural, age,  Livelihood_Income,education, workknowledge,LIlenght, subsidyknow, drinkingwater,cookingwater,farwatermins, wateravail,toilet, house,stove, vehicle, houseown, polposition, LIassociation,polparty, govtscheme, totalincome, Lfarmbigha,  Ipropvalue, Lboat, animals, foodadequacy, foodtrouble,food, healthdist, illness, severeillness)

# Solar dataframe for LSI/ISI with standardized values

# Convert columns to numeric starting from 'education'
cols_to_convert <- names(solar_LI)[which(names(solar_LI) == 'education'):length(names(solar_LI))]
solar_LI[cols_to_convert] <- lapply(solar_LI[cols_to_convert], as.numeric)

# Standardize the values
standardize <- function(x) {
  (x - min(x, na.rm = TRUE)) / (max(x, na.rm = TRUE) - min(x, na.rm = TRUE))
}

solar_LI[cols_to_convert] <- lapply(solar_LI[cols_to_convert], standardize)

# Displaying the first few rows of the dataframe
head(solar_LI)

solar_model <- solar_LI %>%  
  mutate(
    human_asset = rowMeans(dplyr::select(., education, workknowledge, LIlenght), na.rm = TRUE),
    physical_asset = rowMeans(dplyr::select(., drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown), na.rm = TRUE),
    social_asset = rowMeans(dplyr::select(., polposition, LIassociation, polparty, govtscheme), na.rm = TRUE),
    financial_asset = totalincome,
    food_security = rowMeans(dplyr::select(., foodadequacy, foodtrouble, food), na.rm = TRUE),
    health_status = rowMeans(dplyr::select(., healthdist, illness, severeillness), na.rm = TRUE)
  )%>%
  dplyr::select(
    -c(education, workknowledge, LIlenght, 
      drinkingwater, cookingwater, farwatermins, wateravail, toilet, house, stove, vehicle, houseown, 
      polposition, LIassociation, polparty, govtscheme, 
      foodadequacy, foodtrouble, food,
      healthdist, illness, severeillness,
      totalincome, Lfarmbigha, Ipropvalue, Lboat, animals)
  )%>%
  mutate(LIscore = rowMeans(dplyr::select(., human_asset, physical_asset, social_asset,financial_asset, food_security,health_status), na.rm = TRUE))
